Notebook of learning from ensemble labels

### 2021-08-07 docs/manuscript_figures.Rmd
Add option to not predict scores

# Read tiles
guess_tiles <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    pull(tile) %>% unique()
nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
    mutate(guess = ifelse(tile %in% guess_tiles, 1, 0))
samples <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    filter(score > 7)

# Sub-tiling
indices <- matrix(1:64, 8, 8)
indices <- indices[, ncol(indices):1]
sub_tiling <- nicfi_tiles %>% 
    filter(tile == '1228-999') %>% 
    st_make_grid(n = c(8, 8)) %>% 
        st_sf() %>% 
        mutate(index = as.vector(indices))

# Weak labels
labels_esb <- raster(here('data/north/lc_labels_north_mask.tif')) %>% 
    crop( nicfi_tiles %>% filter(tile == '1228-999'))
labels_guess <- raster(
    here('results/north/prediction/classed_1228-999.tif'))

# Sub-tiling figure
sub_tiling_fg <- ggplot(sub_tiling) + 
    geom_sf(color = 'blue', fill = NA, lwd = 0.3) + 
    geom_sf_text(aes(label = index), size = 2.5) +
    theme_minimal() +
    labs(title = 'B') +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.title = element_text(hjust = -0.15, vjust = -6),
          plot.margin = unit(rep(0, 4),"cm"))

# Weak ensemble labels
r_df <- as.data.frame(labels_esb, xy = TRUE) %>%
    rename(`Weak ensemble label` = lc_labels_north_mask) %>% 
    mutate(`Weak ensemble label` = factor(`Weak ensemble label`)) %>% 
    na.omit()
weak_lb_fg <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = `Weak ensemble label`)) +
    scale_fill_manual(
        values = c('#ff7f00', '#33a02c', '#b2df8a',
                   '#074702', '#0ea591'), 
        breaks = c(1, 4, 3, 2, 5),
        labels = c("Cropland", "Shrubland", 
                   "Grassland", "Forest", 'Wetland')) +
    geom_sf(data = sub_tiling, color = 'blue', 
            fill = NA, lty = 'dotted', lwd = 0.4) +
    theme_minimal() +
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))

# RF guessed labels
r_df <- as.data.frame(labels_guess, xy = TRUE) %>%
    rename(`RF guess label` = classed_1228.999) %>% 
    mutate(`RF guess label` = factor(`RF guess label`)) %>% 
    na.omit()
guess_lb_fg <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = `RF guess label`)) +
    scale_fill_manual(
        values = c('#ff7f00', '#074702', '#b2df8a',
                   '#33a02c', '#3347f9', '#5a6057',
                   '#fdbf6f'), 
        breaks = 1:7,
        labels = c("Cropland", 'Forest', "Grassland", 
                   'Shrubland',  "Water", "Urban/Built-up",
                   'Bareland')) +
    geom_sf(data = sub_tiling %>% 
                st_transform(crs(labels_guess)), 
            color = 'blue', 
            fill = NA, lty = 'dotted', lwd = 0.4) +
    theme_minimal() +
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))

# Sample distribution
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = `RF guess label`)) +
    scale_fill_manual('Land cover',
        values = c('#ff7f00', '#074702', '#b2df8a',
                   '#33a02c', '#3347f9', '#5a6057',
                   '#fdbf6f'), 
        breaks = 1:7,
        labels = c("Cropland", 'Forest', "Grassland", 
                   'Shrubland',  "Water", "Built-up",
                   'Bareland')) +
    geom_sf(data = sub_tiling %>% 
                st_transform(crs(labels_guess)), 
            color = 'blue', 
            fill = NA, lty = 'dotted', lwd = 0.4) +
    theme_minimal() +
    theme(legend.position = 'left',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))
legend_lc <- get_legend(legend_lc)

samples_fg <- ggplot() + 
    geom_sf(data = nicfi_tiles,
            aes(color = factor(guess),
                lty = factor(guess)), 
            fill = 'white', lwd = 0.4) +
    scale_linetype_manual('Usage', values = c('solid', 'solid'),
                          labels = c('Others', 'Guessed tile')) +
    scale_color_manual('Usage', values = c("grey", "blue"),
                       labels = c('Others', 'Guessed tile')) +
    geom_sf(data = samples, aes(fill = factor(score)), color = NA) +
    scale_fill_manual('Lable score', 
                      values = c("#00AFBB", "#E7B800", "#FC4E07")) +
    annotation_custom(grob = ggplotGrob(sub_tiling_fg), 
                      xmin = 35.8, xmax = 38.2,
                      ymin = -2.2, ymax = -0.1) +
    labs(title = 'A') +
    theme_minimal() +
    theme(legend.position = 'bottom',
          legend.box = "vertical",
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(-20, 2, 2, 2),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.title = element_text(vjust = -6),
          plot.margin = unit(c(0, 0, 0, 0.2),"cm"))
    # guides(fill = guide_legend(nrow = 2, byrow = TRUE),
    #        color = guide_legend(nrow = 2, byrow = TRUE),
    #        linetype = guide_legend(nrow = 2, byrow = TRUE))

samples_fg <- ggarrange(samples_fg, legend_lc, 
                        nrow = 1, widths = c(1, 0.2))
imgs <- ggarrange(weak_lb_fg, guess_lb_fg, 
                  nrow = 2, labels = c('C', 'D'),
                  font.label = list(face = "plain"),
                  hjust = 0, vjust = 2)
sample_imgs <- ggarrange(samples_fg, imgs, 
                         ncol = 2,
                         widths = c(2.5, 1))
ggsave(here('docs/figures/samples_distribution.png'),
       sample_imgs,
       width = 8, height = 4.5, dpi = 600)
```

@@

## Metrics

```{r}
# Get file names
fns <- list.files(here('results/scalars/single_compose_lr'), 
                  pattern = 'compose_lr',
                  full.names = T)

# Metrics
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
metrics_last10 <- do.call(cbind, lapply(fns, function(fn){
    read.csv(fn, stringsAsFactors = F) %>% 
        dplyr::select(-c(Wall.time, Step)) %>% 
        tail(10)
}))
names(metrics_last10) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

# Calculate mean and sd
items <- c('AA', 'IoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Urban', 'Bareland')
options(digits = 3)
tb <- do.call(rbind, lapply(items, function(item){
    vals <- metrics_last10 %>% pull(all_of(item))
    if (item == 'Urban') item <- 'Built-up'
    data.frame(mean = mean(vals),
               sd = sd(vals)) %>% 
        mutate(metric = item)
}))
```

## Scalars

```{r}
library(here)

# Single U-Net model with step learning rate
# Get file names
fns <- list.files(here('results/scalars/single_step_lr'), 
                  pattern = 'step_lr',
                  full.names = T)

# Learning rate
step_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
    mutate(Step = Step / 113)

# Scalars
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
unet_step_lr_scalars <- lapply(fns, function(fn){
    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
        mutate(Step = Step / 113) %>% 
        dplyr::select(-Wall.time)
})
names(unet_step_lr_scalars) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

# Single U-Net model with compose learning rate
# Get file names
fns <- list.files(here('results/scalars/single_compose_lr'), 
                  pattern = 'compose_lr',
                  full.names = T)

# Learning rate
compose_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
    mutate(Step = Step / 113)

# Scalars
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
unet_compose_lr_scalars <- lapply(fns, function(fn){
    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
        mutate(Step = Step / 113) %>% 
        dplyr::select(-Wall.time)
})
names(unet_compose_lr_scalars) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

# Plot
aa <- merge(unet_compose_lr_scalars$AA, 
            unet_step_lr_scalars$AA, 
            by = 'Step') %>% 
    rename(Compose = Value.x, Cot = Value.y) %>% 
    pivot_longer(cols = c(Compose, Cot),
                 names_to = 'type', values_to = 'value')
ggplot(aa, aes(x = Step, y = value)) +
    geom_line(aes(color = type, lty = type)) +
    geom_smooth(aes(color = type)) +
    theme_bw()
```

>>>>

id_selected <- '1240-995'
# Read tiles
nicfi_tiles <- read_sf(
    here('data/geoms/tiles_nicfi_north.geojson'))

# Sub-tiling
indices <- matrix(1:64, 8, 8)
indices <- indices[, ncol(indices):1]
sub_tiling <- nicfi_tiles %>% 
    filter(tile == id_selected) %>% 
    st_make_grid(n = c(8, 8)) %>% 
    st_sf() %>% 
    mutate(index = as.vector(indices))
trains_inside <- sub_tiling %>% 
    filter(index %in% (read.csv(
    here('results/north/dl_catalog_train.csv'),
    stringsAsFactors = F) %>% 
    filter(tile == id_selected) %>% 
    pull(index))) %>% 
    mutate(Usage = 'Train')
valids_inside <- sub_tiling %>% 
    filter(index %in% (read.csv(
    here('results/north/dl_catalog_valid.csv'),
    stringsAsFactors = F) %>% 
    filter(tile == id_selected) %>% 
    pull(index))) %>% 
    mutate(Usage = 'Validate')
# Labels of each sub-tile
sub_tiles <- rbind(trains_inside, valids_inside) %>% 
    arrange(index); rm(trains_inside, valids_inside)

# Sub-tiling figure
sub_tiling_fg <- ggplot(sub_tiling) + 
    geom_sf(data = sub_tiles, aes(fill = Usage),
            color = 'blue', lwd = 0.3) +
    scale_fill_manual(values = c('forestgreen', 'orangered')) +
    geom_sf(color = 'blue', fill = NA, lwd = 0.3) + 
    geom_sf_text(aes(label = index), size = 2.5) +
    theme_minimal() +
    theme(legend.position = 'bottom',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.title = element_text(hjust = -0.15, vjust = -6),
          plot.margin = unit(rep(0, 4),"cm"))

# Weak labels
labels_esb <- lapply(1:nrow(sub_tiles), function(n){
    raster(here('data/north/lc_labels_north_mask.tif')) %>% 
        crop(sub_tiles %>% slice(n))
}); names(labels_esb) <- sub_tiles$index

labels_guess <- lapply(sub_tiles$index, function(id){
    prefix <- glue('results/north/guess_labels/guess_{id_selected}')
    raster(here(glue('{prefix}_{id}.tif')))
}); names(labels_guess) <- sub_tiles$index

labels_refine <- lapply(sub_tiles$index, function(id){
    prefix <- glue('results/north/refine_labels/{id_selected}')
    raster(here(glue('{prefix}_{id}_label.tif')))
}); names(labels_refine) <- sub_tiles$index

# Plot
color_tb <- data.frame(
    id = 1:7,
    type = c("Cropland", "Forest", 
             "Grassland", "Shrubland", 
             "Water", 'Built-up', "Bareland"),
    color = c('#ff7f00', '#074702', '#b2df8a',
              '#33a02c', '#3347f9', '#5a6057',
              '#fdbf6f'))
plot_rst <- function(rst, bry){
    r_df <- as.data.frame(rst, xy = TRUE) %>%
        `colnames<-`(c('x', 'y', 'rst')) %>%
        mutate(rst = as.factor(rst)) %>% 
        na.omit()
    colors <- color_tb %>% filter(id %in% unique(r_df$rst))

    # plot
    ggplot() + 
        geom_raster(
            data = r_df, 
            aes(x = x, y = y, 
                fill = rst)) +
        scale_fill_manual(
            values = colors %>% pull(color), 
            breaks = colors %>% pull(id),
            labels = colors %>% pull(type)) +
        geom_sf(data = bry, 
                color = 'blue', fill = NA,
                lty = 'dotted', lwd = 0.4) +
        theme_minimal() +
        theme(legend.position = 'none',
              axis.title.x = element_blank(),
              axis.text.x = element_blank(),
              axis.ticks.x = element_blank(),
              axis.title.y = element_blank(),
              axis.text.y = element_blank(),
              axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(),
              plot.margin = unit(rep(0, 4),"cm"))
}

plots_esb <- lapply(1:length(labels_esb), function(n) {
    nm <- names(labels_guess)[n]
    bry <- sub_tiles %>% filter(index == nm)
    plot_rst(labels_esb[[n]], bry)
})

plots_guess <- lapply(1:length(labels_guess), function(n) {
    nm <- names(labels_guess)[n]
    bry <- sub_tiles %>% filter(index == nm) %>% 
        st_transform(crs = crs(labels_guess[[n]]))
    plot_rst(labels_guess[[n]], bry)
})

plots_refine <- lapply(1:length(labels_refine), function(n) {
    nm <- names(labels_refine)[n]
    bry <- sub_tiles %>% filter(index == nm) %>% 
        st_transform(crs = crs(labels_refine[[n]]))
    plot_rst(labels_refine[[n]], bry)
})

# Ensemble plots
## Legend
r_df <- data.frame(x = 1:7, 
                   y = 1:7,
                   rst = as.factor(1:7))
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = rst)) +
    scale_fill_manual('Land cover',
                      values = c('#ff7f00', '#074702', '#b2df8a',
                                 '#33a02c', '#3347f9', '#5a6057',
                                 '#fdbf6f'), 
                      breaks = 1:7,
                      labels = c("Cropland", 'Forest', "Grassland", 
                                 'Shrubland',  "Water", "Built-up",
                                 'Bareland')) +
    theme_minimal() +
    theme(legend.position = 'right',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))+
    guides(fill = guide_legend(ncol = 2))

legend_lc <- get_legend(legend_lc)
sub_tiling_fg <- ggarrange(NULL, sub_tiling_fg, legend_lc, NULL,
                           nrow = 4, heights = c(0.3, 2, 1, 0.3))

esb_fg <- ggarrange(plotlist = plots_esb, ncol = 4,
                    labels = sub_tiles$index, 
                    hjust = -2.5)
guess_fg <- ggarrange(plotlist = plots_guess, ncol = 4)
refine_fg <- ggarrange(plotlist = plots_refine, ncol = 4)
fgs <- ggarrange(esb_fg, guess_fg, refine_fg, nrow = 3,
                 labels = c('A', 'B', 'C'),
                 hjust = 0.4, vjust = 6,
                 font.label = list(face = "plain"))
labels_fg <- ggarrange(NULL, fgs, sub_tiling_fg, 
                       ncol = 3, widths = c(0.1, 2, 1))

ggsave(here('docs/figures/labels.png'),
       labels_fg,
       width = 8, height = 4, dpi = 300)
```

@@

## Results
### Learning rate comparison

```{r}
library(tidyverse)
# Define function
get_curves <- function(experiment_name,
                       step = 59,
                       path = here('results/scalar/compare_lr')){
    # Get file names
    fns <- list.files(path, 
                      pattern = experiment_name,
                      full.names = T)
    fns <- fns[str_detect(fns, 'Validate')]

    # Process each csv
    scalars <- lapply(fns, function(fn){
        scalar <- read.csv(fn, stringsAsFactors = F) %>% 
            mutate(Step = Step / step) %>% # step of each epoch
            dplyr::select(-Wall.time)
    })
    names(scalars) <- gsub(
        '.csv', "", 
        str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

    scalars
}

# Clean scalar csvs
curves_lr_01 <- get_curves('unet_lr_01')
curves_lr_001 <- get_curves('unet_lr_001')
curves_lr_0001 <- get_curves('unet_lr_0001')
curves_lr_00001 <- get_curves('unet_lr_00001')
curves_lr_000001 <- get_curves('unet_lr_000001')

types <- c('AA', 'IoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
        } else{item <- type}
    list(curves_lr_01[[item]],
         curves_lr_001[[item]],
         curves_lr_0001[[item]],
         curves_lr_00001[[item]],
         curves_lr_000001[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '0.1', '0.01', 
                       '0.001', '0.0001', '0.00001')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'Learning rate', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types))

# Get final plot
curves_lr <- ggplot(content, aes(x = Epoch, y = Value)) +
    # geom_line(aes(color = `Learning rate`)) +
    geom_smooth(aes(color = `Learning rate`), span = 0.2,
                se = F, size = 0.6) +
    scale_color_brewer(palette = "Set1") +
    facet_wrap(~Item, scales = 'free_y') +
    labs(y = 'Accuracy') +
    theme_bw() +
    theme(legend.position = 'top')
ggsave(here('docs/figures/curves_lr.png'),
       curves_lr,
       width = 8, height = 5, dpi = 300)
```

### Overall results
#### Metrics
```{r}
library(glue)
# Get file names
fns <- list.files(here(
    file.path('results/scalar',
              'unet_score08_hardiness20_epoch200')), 
    full.names = T)

# Metrics
fns <- fns[str_detect(fns, 'Validate')]
metrics_last10 <- do.call(cbind, lapply(fns, function(fn){
    read.csv(fn, stringsAsFactors = F) %>% 
        dplyr::select(-c(Wall.time, Step)) %>% 
        tail(10)
}))
names(metrics_last10) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z|a-z]{1}[A-Z|a-z]+.csv'))

# Calculate mean and sd
items <- c('loss', 'AA', 'mIoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Urban', 'Bareland')
types <- c('Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland', 'AA')

tb <- do.call(rbind, lapply(items, function(item){
    vals <- metrics_last10 %>% pull(all_of(item))
    if (item == 'Urban') item <- 'Built-up'
    if (item == 'loss') item <- 'Loss'
    data.frame(mean = mean(vals),
               sd = sd(vals)) %>% 
        mutate(Metric = item)
}))

acc <- tb %>% filter(Metric %in% types) %>% 
    mutate(mean = round(mean * 100, 2),
           sd = round(sd * 100, 2),
           Class = factor(Metric, levels = types),
           Accuracy = glue(
               paste0('{format(round(mean, digits = 2), nsmall = 2)}',
                      '\u00B1{format(round(sd, digits = 2), nsmall = 2)} %'))) %>% 
    dplyr::select(Class, Accuracy) %>% 
    arrange(Class)
write.csv(acc, here('docs/figures/acc_last10epoch.csv'),
          row.names = F)
```

#### Scalars

```{r}
library(here)
# Get file names
fns <- list.files(here(
    file.path('results/scalar',
              'unet_score08_hardiness20_epoch200')), 
    full.names = T)

step <- 59
# Learning rate
lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
    mutate(Epoch = Step / step)

# Scalars
fns <- fns[str_detect(fns, 'Validate|Train_lr')]
final_mod_scalars <- lapply(fns, function(fn){
    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
        mutate(Epoch = Step / step) %>% 
        dplyr::select(-c(Wall.time, Step))
})
names(final_mod_scalars) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z|a-z]{1}[A-Z|a-z]+.csv'))

types <- c('Learning rate', 'Loss', 'AA', 'mIoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
lc <- c('Cropland', 'Forest', 
        'Grassland', 'Shrubland', 'Water', 
        'Built-up', 'Bareland', 'AA')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
    } else if (type == 'Loss'){
        item <- 'loss'
    } else if (type == 'Learning rate'){
        item <- 'lr'
    } else {item <- type}
    final_mod_scalars[[item]] %>% 
        mutate(Item = type)
}))

# Plot
curve_lr <- content %>% 
    filter(Item == 'Learning rate') %>% 
    mutate(Value = Value * 1000) %>% 
    ggplot(., aes(x = Epoch, y = Value)) +
    geom_line() +
    labs(y = expression(Learning ~ rate ~ (10^-3)), x = '') +
    theme_bw()
curve_loss <- content %>% 
    filter(Item == 'Loss') %>% 
    ggplot(., aes(x = Epoch, y = Value)) +
    geom_line() +
    labs(y = 'Loss', x = '') +
    theme_bw()
curve_iou <- content %>% 
    filter(Item == 'mIoU') %>% 
    ggplot(., aes(x = Epoch, y = Value)) +
    geom_line() +
    labs(y = 'mIoU', x = '') +
    theme_bw()
curves_acc <- content %>% 
    filter(Item %in% lc) %>% 
    mutate(Item = factor(Item, levels = lc)) %>% 
    ggplot(aes(x = Epoch, y = Value)) +
    geom_line() +
    labs(y = 'Accuracy') +
    facet_wrap(~Item, scales = 'free_y', 
               nrow = 2, ncol = 4) +
    theme_bw()
curves <- ggarrange(
    ggarrange(curve_lr, curve_loss, curve_iou, ncol = 3),
    curves_acc, nrow = 2, heights = c(1, 1.6))

ggsave(here('docs/figures/curves_final_mod.png'),
       curves,
       width = 8, height = 5, dpi = 300)
```

## Sensitivity analysis
### Quality weights
#### Score factor
```{r}
# Clean scalar csvs
curves_no_weight <- get_curves(
    'unet_no_weight',
    path = here('results/scalar/compare_score'))
curves_score02 <- get_curves(
    'unet_score_02',
    path = here('results/scalar/compare_score'))
curves_score08 <- get_curves(
    'unet_score_08',
    path = here('results/scalar/compare_score'))
curves_score16 <- get_curves(
    'unet_score_16',
    path = here('results/scalar/compare_score'))
curves_score32 <- get_curves(
    'unet_score_32',
    path = here('results/scalar/compare_score'))
curves_score100 <- get_curves(
    'unet_score_100',
    path = here('results/scalar/compare_score'))

types <- c('AA', 'IoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
        } else{item <- type}
    list(curves_no_weight[[item]],
         curves_score02[[item]],
         curves_score08[[item]],
         curves_score16[[item]],
         curves_score32[[item]],
         curves_score100[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '0', '0.2', '0.8', 
                       '1.6', '3.2', '10')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'Weight factor', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types),
               `Weight factor` = factor(
                   `Weight factor`, 
                   levels = c('0', '0.2', '0.8', 
                              '1.6', '3.2', '10')))

# Get final plot
curves_score <- ggplot(content, aes(x = Epoch, y = Value)) +
    # geom_line(aes(color = `Weight factor`)) +
    geom_smooth(aes(color = `Weight factor`), span = 0.2,
                se = F, size = 0.6) +
    scale_color_manual(
        values = c('Black', 
                   RColorBrewer::brewer.pal(5, "Dark2"))) +
    # scale_color_brewer(palette = "Dark2") +
    facet_wrap(~Item, scales = 'free_y') +
    labs(y = 'Accuracy') +
    theme_bw() +
    theme(legend.position = 'top') +
    guides(color = guide_legend(nrow = 1))
ggsave(here('docs/figures/curves_score.png'),
       curves_score,
       width = 8, height = 5, dpi = 300)
```

#### Hardiness
```{r}
# Clean scalar csvs
curves_score08_nohard <- get_curves(
    'unet_score_08',
    path = here('results/scalar/compare_score'))
curves_hard2 <- get_curves(
    'unet_score08_hardiness_2',
    path = here('results/scalar/compare_score'))
curves_hard4 <- get_curves(
    'unet_score08_hardiness_4',
    path = here('results/scalar/compare_score'))
curves_hard6 <- get_curves(
    'unet_score08_hardiness_6',
    path = here('results/scalar/compare_score'))

types <- c('AA', 'IoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Built-up', 'Bareland')
content <- do.call(rbind, lapply(types, function(type){
    if (type == 'Built-up') {
        item <- 'Urban'
        } else{item <- type}
    list(curves_score08_nohard[[item]],
         curves_hard2[[item]],
         curves_hard4[[item]],
         curves_hard6[[item]]) %>% 
        reduce(left_join, by = "Step") %>% 
        `colnames<-`(c("Epoch", '0', '2', '4', '6')) %>% 
        mutate(Item = type) %>% 
        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
                     names_to = 'Weight scale', 
                     values_to = 'Value')
})) %>% mutate(Item = factor(Item, levels = types),
               `Weight scale` = factor(
                   `Weight scale`, 
                   levels = c('0', '2', '4', '6')))

# Get final plot
curves_hard <- ggplot(content, aes(x = Epoch, y = Value)) +
    geom_smooth(aes(color = `Weight scale`), span = 0.2,
                se = F, size = 0.6) +
    scale_color_manual(
        values = c('Black', 
                   RColorBrewer::brewer.pal(3, "Dark2"))) +
    # scale_color_brewer(palette = "Dark2") +
    facet_wrap(~Item, scales = 'free_y') +
    labs(y = 'Accuracy') +
    theme_bw() +
    theme(legend.position = 'top') +
    guides(color = guide_legend(nrow = 1))
ggsave(here('docs/figures/curves_hard.png'),
       curves_hard,
       width = 8, height = 5, dpi = 300)
```

### Sampling

```{r}

```

### 2021-08-07 docs/notebook_learn_dl_ensemble.Rmd
Overfitting
Add option to not predict scores

scp -r /Users/pinot/Dropbox/research/hrlcm/results/north/norm_stats ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north

scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train.csv ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north

scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_valid.csv ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
```

@@

```
python hrlcm/fit_step_lr.py --exp_name unet_slr --num_workers 32 --gpu_devices '0,1,2,3'
```

```
python hrlcm/fit_compose_lr.py --exp_name unet_clr --num_workers 32 --gpu_devices '0,1,2,3'
```

@@

```
python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

@@

```
python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```

>>>>

scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_1.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_2.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_random_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_random_67.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv
```

@@

```
python hrlcm/fit_step_lr.py --exp_name unet_one_tile --num_workers 32 --gpu_devices '0,1,2,3'
```

```
python hrlcm/fit_compose_lr.py --exp_name unet_score08_hardiness2_epoch300 --num_workers 32 --gpu_devices '0,1,2,3'
```

@@

```
python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200
```

@@

```
scp /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200/checkpoints/final.pth ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/dl/final.pth;
scp /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200/checkpoints/args.pkl ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/dl/args.pkl

python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/evaluation /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200
```
